# Week 7 Short Answer Questions

## Gretchen Greene

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

15.1, 15.2,
16.1, 16.2, 16.3

15.1)
- mdy()
- mdy()
- dmy()
- mdy_hm(
- mdy()

15.2)
a) tidyr::extract_numeric() will work correctly
b) tidyr::extract_numeric()
c) as.numeric() will work correctly
d)tidyr::extract_numeric()
e) as.numeric()
f)tidyr::extract_numeric()
g) neighter will work. There are characters and symbols in the string
h)tidyr::extract_numeric()
i)tidyr::extract_numeric()

16.1)
```{r}
BabyNames %>%
  filter( sex == "M") %>%
  group_by(name) %>%
  summarise (total = sum (count)) %>%
  filter (grepl("[aeiou]$", name)) %>%
  arrange( desc(total)) %>%
  head(10)
```

1. George, 2. Joshua, 3. Jose, 4. Kyle, 5. Lawrence, 6. Joe, 7. Willie, 8. Jesse, 9. Bruce, 10. Eugene

```{r}
BabyNames %>%
  group_by(name)%>%
  summarise (total =sum(count)) %>%
  filter(grepl(".*(jo$|joe$)", name))%>%
  arrange (desc(total))%>%
  head(10)
```
1. Maryjo 2. Billiejo 3. Marijo 4. Bobbijo 5. Bobbiejo, 6. Bettyjo, 7. Alejo 8. Amyjo 9. Billyjoe, 10. Jojo

16.2)
One digit from 0 to 9 is pulled out followed by two digits from 0 to 9. Then any character of either a space, period, or dash. Then three characters from 0 to 9. Then four characters from 0 to 9.

16.3)
1. Two letter strings
2. For the pattern A[LKSZRAP] there are seven matching strings. For D[EC] there are two strings. There are 61 total patterns
3. These are the two letter abbreviations for US states and territories. 