# Week 6 Short Answer Questions

## Gretchen Greene

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(mosaicData)
```
<!-- put your content after this line -->

12.1, 12.2, 12.3
13.1, 13.2, 13.3, 13.4
14.1, 14.3, 14.7, 14.10

12.1)
```{r}
BabyNames %>%
  group_by(sex, name) %>%
  summarise( total = sum (count)) %>%
  mutate(namescore= rank(desc(total)))%>%
  filter(namescore <=5)
```
top 5 female names: Mary, Elizabeth, Patricia, Jennifer, Linda
top 5 male names: James, John, Robert, Michael, William

12.2)
```{r}
PopularCounts <-
  BabyNames %>%
  group_by(year,name)%>%
  summarise(count = sum(count))%>%
  mutate(frac_in_top_100 = rank(desc(count)) <= 100) %>%
  group_by(year, frac_in_top_100)%>%
  summarise(total = sum(count))

GlyphReady <-
  PopularCounts %>%
  spread(frac_in_top_100, total)%>%
  mutate(frac_in_top_100 = `TRUE`/(`TRUE` + `FALSE`))

GlyphReady %>%
  ggplot(aes(x=year, y= frac_in_top_100)) + geom_line() + ylim(0,NA)
```

12.3)
a) summary function
b) neither summary nor transformation. It is a pair of values not a single value which is necessary for a summary function
c) summary function
d) transformation function
e) transformation function
f) summary function
g) transformation function
h) summary function. The whole set of dates is turned into a single value.

13.1) 
1) 7 verticies; China, germany, France, UK, Italy, USA, USSR
2) 9 edges

13.2) 
1) A, C, B, D
2) Table 2
3) Table 1 shows an ede from B to C but there is no edge between B and C. Table 3 shows an edge between three points. Edges only are between 2 vertices.

13.3)
Table 2 gives the information needed to draw the graph shown.

13.4) 
1. Exports is mapped to the size of the letter.
2. Pop is mapped to the shape of the gray symbol. 

14.1)
```{r}
mosaicData::CPS85 %>%
  ggplot(aes(x = sex, y= wage)) + geom_boxplot(aes(fill= sex))
```

14.3) The most likely hieght for women is around 1.55 m and for men around 1.7 m.

14.7) 
```{r}
mosaicData::CPS85 %>%
  ggplot(aes(x =educ, y= wage, color= sex)) +
  geom_point() + 
  stat_smooth(method = "lm") + 
  ylim (0, 15)
```

14.10)
```{r}
mosaicData::Galton %>%
  ggplot( aes( x= height, group = sex)) + 
  geom_density( aes( color = sex, fill = sex, alpha = 0.5))
```