# Week 3 Project

## Gretchen Greene 

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(mosaicData)
```
<!-- put your content after this line -->

----Figure 1....

```{r}
ggplot(data = CPS85, aes(x = exper, y = wage, color = married)) + geom_point() + facet_wrap( ~ sector)
```
What mode of graphic is it?
A scatter plot

What variables from the respective data tables are involved?
The variables involved are experience, Wage, married, sector

What role each of those variables plays in the graphic?
The x-axis is exper level, wage is the y variable, the graphic is faceted by sector, and it is colored by married or not


Figure 2
```{r}
ggplot(data = NCHS, aes(x = bmi)) + geom_density(aes(fill = sex, alpha= 0.5)) + facet_wrap(~pregnant)
```
What mode of graphic is it?
Figure 2 is a density plot

What variables from the respective data tables are involved?
The variables involved are density, bmi, sex, and pregnant or not.

What role each of those variables plays in the graphic?
bmi is the measured quantity mapped along the x-axis. The y axis corresponds to density which is the number of cases corresponding to each x value. The color corresponds to pregnant yes or no.

In Figure 2, why is there no data variable being used for the y-axis?
There is no variable becuase it is a density plot. Density is the y axis.

Wrangling
```{r}
help("diamonds")
```
1. Which color diamonds seem to be largest on avergage?
```{r}
diamonds%>%
  group_by(color)%>%
  summarize(size = mean(carat)) %>%
  arrange(desc(size))%>%
  head(1)
```
Color J has the largest on average size of 1.16137

2. Which clarity of diamonds has the largest average "table" per carat?
```{r}
diamonds%>%
  group_by(clarity)%>%
  summarize(avgtable=mean(table))%>%
  arrange(desc(avgtable))%>%
  head(1)
```
11 has the largest avgtable of 58.30378

Voting:
```{r}
Minneapolis2013 %>% nrow()
```
1. 80101 cases
```{r}
Minneapolis2013 %>%
  group_by(Second) %>%
  summarise(votes=n()) %>%
  arrange(desc(votes)) %>%
  head(5)
```
2. The top 5 canidates in the second vote selesctions were: Betsy Hodges, Don Samuels, Mark Andrew, undervote, Jackie Cherryhomes

```{r}
Minneapolis2013 %>%
  filter(First =='undervote')%>%
  tally()

Minneapolis2013 %>%
  filter(Second == 'undervote') %>%
  tally()

Minneapolis2013 %>%
  filter(Third == 'undervote') %>%
  tally()
```
3. a) 834 undervotes in first choice
b) 10598 undervotes in second choice
c) 19210 undervotes in third choice 
```{r}
Minneapolis2013 %>% 
  filter(First=='BETSY HODGES') %>%
  group_by(Second)%>%
  summarise(votes=n())%>%
  arrange(desc(votes))%>%
  head(3)
```
4. top 3 second vote selesctions among people who voted for Betsy Hodges: 1. Mark Andrew: 8787 votes, 2. Don Samuels: 8743 votes, 3. Jackie Cherryhomes: 2563 votes

```{r}
Minneapolis2013 %>%
  group_by(Precinct) %>%
  summarise(fraction = base::mean(First=='undervote')) %>%
  arrange(desc(fraction))%>%
  head(1)
```
  5. Precinct P-6C had the highest fraction of First vote selections marked as "undervote".