# Week 3 Project

## Gretchen Greene 

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(mosaicData)
```
<!-- put your content after this line -->

What mode of graphic is it?
Figure 1 shows a display of distribution. 

What variables from the respective data tables are involved?
The variables involved are density, bmi, sex, and pregnant or not.

What role each of those variables plays in the graphic?
bmi is the measured quantity mapped along the x-axis. The y axis corresponds to density which is the number of cases corresponding to each x value. The color corresponds to pregnant yes or no.

In Figure 2, why is there no data variable being used for the y-axis?
----No figure 2....

```{r}
#ggplot(data = CPS85, aes(x = ????, y = ????, color = ????)) + geom_point() + facet_wrap( ~ ????)

ggplot(data = NCHS, aes(x = bmi) + geom_density(aes(color = 'red)) + facet_wrap(sex)
```
Wrangling
```{r}
help("diamonds")
```
1. Which color diamonds seem to be largest on avergage?
```{r}
diamonds%>%
  group_by(color)%>%
  summarise(size=mean(carat))%>%
  arrange(desc(size))%>%
  head(1)
```
J..?
2. Which clarity of diamonds has the largest average "table" per carat?
```{r}
diamonds%>%
  group_by(clarity)%>%
  summarize(avgtable=mean(table))%>%
  arrange(desc(avgtable))%>%
  head(1)
```
11..?

Voting:
```{r}
Minneapolis2013%>%
  summarise(total=n())
```
1. 80101 cases
2. 
```{r}
help("Minneapolis2013")
Minneapolis2013%>%
  
```
